### 2015-01-27 cav-2015-tex/rw.tex
Re-worked the introduciton, added section for a high-level description of the method, added more to related work section.

To address the issue of references, several projects have generalized
the core idea of symbolic execution, enabling it to be applied to
programs with more general types, including references and
arrays~\cite{GSE03,KiasanKunit,Rosner:2015}. However, these generalized symbolic execution (GSE) techniques universally require nondeterministic case-splitting during dereferencing operations, thus exacerbating the path explosion problem. Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during
symbolic execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths than
GSE techniques.

@@

Dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically. ~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously. When the program reaches a statement that cannot be reasoned about symbolically, it substitutes in values from the concrete execution and continues. When reaching the end of a program path, DSE inverts the branch conditions and uses the solver to generate concrete inputs for another execution path. While concretization allows DSE to explore a much wider selection of programs, this freedom comes at the price of completeness. The process of concretization introduces approximation such that

In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them. A number of DSE techniques use concretization when reasoning about references ~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis. The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}. However, the heap model in SAGE requires fixing the size of the memory prior to starting the analysis, and is therefore not complete.

\noindent\textbf{Bounded Model Checking}
Bounded model checking (BMC) techniques seek to avoid the path explosion problem by converting an entire program execution, along with its specifications, into a constraint problem called a verification condition. The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis. Many BMC methods include a model for reasoning about references, including those described in ~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis. By extension, the reference models used in BMC methods are generally not complete. Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.

\noindent\textbf{Static Analysis}

\noindent\textbf{Symbolic Heap Representations}
% a good place to mention procedure summaries, like Yorsh and the Dilligs.
Our work builds upon a number of prior techniques that use sets of guarded values to represent program state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references. While symbolic referencing operations could be supported in principle with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing. All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} do not perform a complete analysis.

>>>>

To address the issue of references, several projects have generalized
the core idea of symbolic execution, enabling it to be applied to
programs with more general types, including references and
arrays~\cite{GSE03,KiasanKunit,Cadar:2008,Rosner:2015}. However, these generalized symbolic execution (GSE) techniques work by branching over multiple copies of the system state during dereferencing operations, thus exacerbating the path explosion problem. Our work leverages the core idea in generalized symbolic execution
with lazy initialization to construct the heap on-the-fly during
symbolic execution, but avoids the nondeterminism introduced by GSE by
constructing a summary heap and will generally create fewer paths than
GSE techniques.

@@

Dynamic symbolic execution (\dsetxt{}, sometimes referred to as concolic execution) has emerged as a way to enable symbolic execution to continue on programs that contain elements that cannot be reasoned about symbolically. ~\dsetxt{} works by executing a program using concrete and symbolic engines simultaneously. When the program reaches a statement that cannot be reasoned about symbolically, it substitutes in values from the concrete execution and continues. When reaching the end of a program path, DSE inverts the branch conditions and uses the solver to generate concrete inputs for another execution path. While concretization allows DSE to explore a much wider selection of programs, this freedom comes at the price of completeness. The process of concretization introduces approximation such that all possible execution paths may not be explored.

In the absence of an effective theory of references, DSE has been a natural choice for reasoning about programs that contain them. A number of DSE techniques use concretization when reasoning about references ~\cite{Godefroid:2005,Sen:2005,Godefroid:POPL07,Tillmann:2008}. However, as demonstrated in \ref{fig:DSEtest}, DSE underapproximates when it concretizes symbolic values, resulting in an incomplete analysis. The SAGE DSE engine~\cite{Elkarablieh:2009} includes more sophisticated methods for reasoning about references, and can successfully reason about the example in \ref{fig:DSEtest}. However, the heap model in SAGE requires fixing the size of memory prior to starting the analysis, and is therefore not complete.

\noindent\textbf{Bounded Model Checking}
Bounded model checking (BMC) techniques seek to avoid the path explosion problem by converting an entire program execution, along with its specifications, into a constraint problem called a verification condition. The advantage in creating a single constraint is that SMT solvers can often reason more efficiently about all paths simultaneously rather than on a case-by-case basis. Many BMC methods include a model for reasoning about references, including those described in ~\cite{Clarke:2004,Barnett:2006,Xie:2005,Babic:2007,Dillig:2011}. However, BMC techniques are not complete for general programs, due to the need to set an execution path-length bound prior to conducting the analysis. By extension, the bounded reference models used in BMC methods are generally not complete. Other limitations include assuming that symbolic references do not alias~\cite{Xie:2005,Babic:2007}, that data structures are not recursive~\cite{Dillig:2011}, or requiring that symbolic references are never dereferenced~\cite{Clarke:2004}.

\noindent\textbf{Symbolic Heap Representations}
A number of techniques use summary heap representations that are not sound. These models can greatly reduce the complexity of dereferencing queries, but do not allow.
% a good place to mention procedure summaries, like Yorsh and the Dilligs.
Our work builds upon a number of prior techniques that use sets of guarded values to represent program state~\cite{Sen:2014,Torlak:2014,Yorsh:2008,Xie:2005,Dillig:2011,Elkarablieh:2009}. The methods presented in~\cite{Sen:2014,Torlak:2014,Yorsh:2008} use value sets to represent all symbolic program state, including references. While symbolic referencing operations could, in principle, be supported with these methods, it is not clear from the published material exactly how that might be accomplished, especially in the case of dereferencing. All of the methods presenting solutions to the dereferencing problem~\cite{Xie:2005,Dillig:2011,Elkarablieh:2009} are not complete, because they require setting a bound on the size of the input heap prior to conducting the analysis.
